Einstein's gravity from a polynomial affine model

### 2016-05-03 MS.tex
Several modifications. Comments about future changes

At this stage, we have proved that \emph{any spherically symmetric (metric) solution of the Eqs.~\eqref{SimpleEOM} is necessarily static}, which is one of the main statements of Birkhoff's theorem. This result, simplifies the Eq.~\eqref{hugeeq} and makes clearer the necessity of setting $A(r) = B(r)$ to solve the equations of motion. Finally, according to Eq.~\eqref{simplef} the general (metric) solution is the (Anti-)de-Sitter--Schwarzschild metric.

>>>>

At this stage, we have proved that \emph{any spherically symmetric (metric) solution of the Eqs.~\eqref{SimpleEOM} is necessarily static}, which is one of the main statements of Birkhoff's theorem.

This result, simplifies the Eq.~\eqref{hugeeq} but the equations are still non-linear. However, one can get ride off the non-linearity by setting $A(r) = B(r)$. In this \emph{linearized} regime, according to Eq.~\eqref{simplef} the general (metric) solution is the (Anti-)de-Sitter--Schwarzschild metric.

Although we restricted ourselves to the \emph{linearized} regime of the field equations, it is possible to go a bit further in the nonlinear regime. As a preliminary result~\cite{OCF-future2}, we have found that using the Frobenius methods with a Laurent series expansion, the leading order of the solutions is three-fold in the radial coordinate. These solutions correspond to the pairs given by $(\alpha,\beta)$---$\alpha$ (resp. $\beta)$ is the leading order of the series expansion for the function $A(r)$ (resp. $B(r)$)---equals to $(-1,-1)$, $(2,-2)$ and $(-2,2)$.
%%Two of these branches coincide with the reciprocal and quadratic dependence on $r$ of $A$ and $B$, while the third one gives novel dependence,
%% \begin{equation}
%%   A(r) = 1 + \frac{\alpha}{r} + \beta r^2 + \frac{\gamma}{r^2},
%% \end{equation}
%% and
%% \begin{equation}
%%   B(r) = 1 + \frac{\alpha}{r} + (\beta + \gamma) r^2.
%% \end{equation}
